The FAIRification of research in real-world evidence: A practical introduction to reproducible analytic workflows using Git and R

### 2023-11-22 manuscript/manuscript.qmd
introduced tagging as per R#2 comment

@@

This step is not needed if the intention of a researcher is just to keep track of local changes and there is no wish to share code, collaborate with others or work across different systems. However, most of the times researchers use `Git` particularly for the purpose of collaborating on a project as depicted in @fig-collaborate.

@@

>>>>

### Tags (`tag`) {#tags}

A handy `Git` feature to highlight particularly important commits, snapshots, code/software releases or milestones of a project is `tagging`. In context of RWE studies, this can be a specific version of an analysis, e.g., the one used for regulatory submission or completion of a manuscript version or revision.

Tags can be annotated with a semantic identifier and tag message, e.g.,

```{bash}
git tag -a v2.0 -m "Revised (R1) manuscript version"
```

All created tags can be displayed using the following command:

```{bash}
git tag
```

@@

Tags, as described in @sec-tags, need to be separately pushed, e.g.,

```{bash}
git push origin v1.0
```

In summary, `git push` is not needed if the intention of a researcher is just to keep track of local changes and there is no wish to share code, collaborate with others or work across different systems. However, most of the times researchers use `Git` particularly for the purpose of collaborating on a project as depicted in @fig-collaborate.

@@

Besides the usage of `Git` and remote repositories as a version control systems, there are also further relevant aspects that determine the reproducibility of analytic code when using open-source software such as R. To complement the introduction and discussion on `Git` in this manuscript, section 2 (*Reproducible computation environments in R*) in the **Supplementary Material** provides a few further considerations addressing the computational reproducibility when using R.
